### 2025-09-07 submissions/03-jpam-RR/submit_journal.tex
addressed R1's comments

    \begin{spacing}{\rrxspc}
            \textbf{Response:} I thank the referee for this suggestion. I agree that using more granular geographic units would provide a more precise measure of local bias. However, there are major data limitations that prevent me from doing so. First, the CPS does not provide geographic identifiers below the county level and only for 45\% of the sample and only for counties with larger populations. Therefore, if used at the county level, I would lose more than half of the sample and potentially introduce bias. Second, even if I had access to more granular geographic identifiers in the CPS, to my knowledge, there are no measures of racial bias at more granular geographic levels. The General Social Survey (GSS), which I use as one of my measures of racial bias, is only representative at the the state level. The American National Election Studies (ANES) is only available at the state level. The Uniform Crime Reports (UCR), which I use to calculate anti-Asian hate crimes, is recommended to not be used at the county level and is not available at lower levels. The Implicit Association Test (IAT) data is the only dataset that available at the county level, however, many social scientists have raised concerns about using the IAT on it's own. Therefore, while I agree with the referee that using more granular geographic units would be ideal, I am limited by data availability. I will add a paragraph to the conclusion discussing this limitation and suggesting that future research could explore this question using more granular geographic units if data becomes available. Specifically, I will add the following paragraph to the conclusion: ``More granular geographic units, such as counties, city, or zip-code level, could provide a more precise measure of local bias. However, data limitations prevent the use of these finer geographic levels in the current analysis. Future research could explore this question using more detailed geographic identifiers if such data becomes available, allowing for a deeper understanding of how local contexts shape racial identity.''
    \end{spacing}

@@

@@

    \begin{spacing}{\rrxspc}
       Thank you for this important methodological observation. You raise a valid point about the conceptual alignment between my bias measures and outcomes. Let me clarify my approach: The ANES racial animus questions do primarily focus on attitudes toward Black Americans, I also use measures of animus toward Asian Americans. Research consistently shows that racial prejudices are highly correlated across different minority groups—individuals who express bias toward one racial minority typically hold similar attitudes toward others \autocite{almasalkhi2023links, mora2020antiblackness}. These measures therefore capture general patterns of racial animus rather than group-specific bias alone. Crucially, my composite bias index combines three distinct components: (1) Asian-focused IAT measures, (2) ANES racial animus questions, and (3) hate crimes specifically targeting Asian Americans. This multi-proxy approach effectively weights the overall bias measure toward Asian-specific prejudice (two of three components directly measure anti-Asian sentiment) while incorporating information about the broader racial climate through the ANES measures. This methodological choice serves two purposes: it reduces measurement error through the composite approach while capturing both specific anti-Asian bias and the general environment of racial prejudice that affects all minority groups. 
    \end{spacing}
    \clearpage
    \pagebreak

@@

        \begin{spacing}{\rrxspc}

    \end{spacing}

@@

        \begin{spacing}{\rrxspc}

    \end{spacing}

>>>>

    \begin{spacing}{\rrxspc}
            \textbf{Response:} I thank the referee for this suggestion. I agree that using more granular geographic units would provide a more precise measure of local bias. However, there are major data limitations that prevent me from doing so. First, the CPS does not provide geographic identifiers below the county level and only for 45\% of the sample and only for counties with larger populations. Therefore, if used at the county level, I would lose more than half of the sample and potentially introduce bias. Second, even if I had access to more granular geographic identifiers in the CPS, to my knowledge, there are no measures of racial bias at more granular geographic levels. The General Social Survey (GSS), which I use as one of my measures of racial bias, is only representative at the the state level. The American National Election Studies (ANES) is only available at the state level. The Uniform Crime Reports (UCR), which I use to calculate anti-Asian hate crimes, is recommended to not be used at the county level and is not available at lower levels. The Implicit Association Test (IAT) data is the only dataset that available at the county level, however, many social scientists have raised concerns about using the IAT on it's own. Therefore, while I agree with the referee that using more granular geographic units would be ideal, I am limited by data availability. I will add a paragraph to the conclusion discussing this limitation and suggesting that future research could explore this question using more granular geographic units if data becomes available. Specifically, I will add the following paragraph to the conclusion: ``More granular geographic units, such as counties, city, or zip-code level, could provide a more precise measure of local bias. However, data limitations prevent the use of these finer geographic levels in the current analysis. Future research could explore this question using more detailed geographic identifiers if such data becomes available, allowing for a deeper understanding of how local contexts shape racial identity.''

            To strengthen how I address this concern, I have conducted supplemental analyses using county-level and MSA-level Implicit Association Test (IAT) data, which are available at more granular geographic levels than the state-level measures used in the main analysis. These results are presented in Appendix Figures \ref{plot01-regression-gen-county}, \ref{plot01-regression-byparent-county}, \ref{plot01-regression-gen-msa}, and \ref{plot01-regression-byparent-msa}. The patterns observed at the county and MSA levels are consistent with the main state-level findings, showing similar negative relationships between anti-Asian bias and Asian identity reporting across generations and parental types. While these analyses are limited to IAT measures alone (due to data availability constraints for other bias measures at sub-state levels), they provide additional evidence that the documented relationships hold at more localized geographic scales. I have also added a footnote in the main results section directing readers to these supplemental analyses. The footnote reads: ``I show the results using county-level and MSA-level anti-Asian bias measures from the Implicit Association Test (IAT) show similar patterns. I present the county-level results in Figures \ref{plot01-regression-gen-county} and \ref{plot01-regression-byparent-county}, while I show the MSA-level in Figures \ref{plot01-regression-gen-msa} and \ref{plot01-regression-byparent-msa}.''
    \end{spacing}

@@

    \begin{spacing}{\rrxspc}
        \textbf{Response:} Thank you so much for this important suggestion. I agree that examining the relationship between bias and racial identity among adults would provide valuable insights into how these dynamics evolve over the life course. To address this comment, I have conducted supplemental analyses using the same empirical strategy on an adult sample (ages 18 and above) from the CPS. I show the summary statistics for the adult sample in Table (\ref{tab:sumstat-adults}) and the ethnic attrition for first- and second-generation Asian adults in Table (\ref{tab:hispbygen-adults}). Moreover, I present the relationship between anti-Asian bias and self-reported Asian identity among adults in Figures \ref{plot01-regression-gen-adults} and \ref{plot01-regression-byparent-adults}. The results indicate that the negative relationship between anti-Asian bias and Asian identity reporting among adults mirrors the patterns observed in children, suggesting that similar identity calculations are at play across age groups.

        I also added the following two discussion of the results in the main text. First: ``I report the results using adult samples in Figure (\ref{plot01-regression-gen-adults}). I present results estimating the main specification for all adults in panel (A) and for first- and second-generation subsamples in panels (B) and (C), respectively. Anti-Asian bias and Asian racial identity reporting exhibit negative associations. One standard deviation anti-Asian bias increases correlate with 5 percentage point decreases in Asian racial identity reporting. Among first-generation Asian American adults, one standard deviation anti-Asian bias increases associate with 2 percentage point decreases in Asian racial identity reporting but is statistically insignificant. Among second-generation Asian American adults, one standard deviation anti-Asian bias increases associate with 13 percentage point decreases in Asian racial identity reporting. '' Second: ``I report the results using adult samples in Figure (\ref{plot01-regression-byparent-adults}). I present results estimating the main specification for all second-generation adults in panel (A) and for AA, AW, and WA children subsamples in panels (B), (C), and (D), respectively. One standard deviation anti-Asian bias increases associate with 13 percentage point decreases in Asian racial identity reporting among second-generation adults. Among second-generation adults with endogamous parents, one standard deviation anti-Asian bias increases associate with 10 percentage point decreases in Asian racial identity reporting but are statistically insignificant. However, one standard deviation anti-Asian bias increases associate with a statistically insignificant 3 percentage point decreases in Asian racial identity reporting among Asian father-White mother adults, and 24 percentage point decreases among White father-Asian mother adults.''
    \end{spacing}

@@

    \begin{spacing}{\rrxspc}
       \textbf{Response:} Thank you for this important methodological observation. You raise a valid point about the conceptual alignment between my bias measures and outcomes. Let me clarify my approach: The ANES racial animus questions do primarily focus on attitudes toward Black Americans, I also use measures of animus toward Asian Americans. Research consistently shows that racial prejudices are highly correlated across different minority groups—individuals who express bias toward one racial minority typically hold similar attitudes toward others \autocite{almasalkhi2023links, mora2020antiblackness}. These measures therefore capture general patterns of racial animus rather than group-specific bias alone. Crucially, my composite bias index combines three distinct components: (1) Asian-focused IAT measures, (2) ANES racial animus questions, and (3) hate crimes specifically targeting Asian Americans. This multi-proxy approach effectively weights the overall bias measure toward Asian-specific prejudice (two of three components directly measure anti-Asian sentiment) while incorporating information about the broader racial climate through the ANES measures. This methodological choice serves two purposes: it reduces measurement error through the composite approach while capturing both specific anti-Asian bias and the general environment of racial prejudice that affects all minority groups. 
    \end{spacing}
    \clearpage
    \pagebreak

@@

@@

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 7. 
        \end{quotation}
        \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 8. 
        \end{quotation}
        \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 9. 
        \end{quotation}
        \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 10. 
        \end{quotation}
        \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 11. 
        \end{quotation}
        \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 12. 
        \end{quotation}
        \end{spacing}

    \begin{spacing}{\rrquote}
        \begin{quotation}
        \textbf{R2: } 13. 
        \end{quotation}
        \end{spacing}
